Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
mini mine moe

A number of research PIM systems have demonstrated numerous ways that users can benefit from better data integration support.  For example, SEMEX's \cite{semex} rich uniform query interface allowed users to quickly trace references of people, places and things across files, folders and repositories.  Similarly, Haystack, a personal information platform, allowed users to visualise and customise how they worked with their data in a uniform, consolidated manner \cite{haystack}. Pertaining to each system's ability to integrate information from arbitrary new data sources, however, both systems generally required new sources to either already conform to a pre-specified set of ontologies, or have the user provide a manual specify such a mapping translation themselves.

@@

\section{Pre-studies: The Need for and Challenges in realising Ad-Hoc Data Integration in PIM Tools}

@@

In summary, while data records ranged in complexity, no data source subsumed the rest; all contained properties that other sources did not have.  Moreover, the most common types of heterogeneity exhibited were terminological and value-related, although simpler kinds of structural heterogeneity (pertaining to representing substructures of values) were also common.

>>>>

A number of research PIM systems have demonstrated how users benefit from unified, integrated data models.  SEMEX's \cite{semex} uniform query interface allowed users to quickly trace references of people, places and things across files, folders and repositories.  Similarly, Haystack, allowed users to visualise and customise how they worked with their data in a uniform, consolidated manner \cite{haystack}. 
% Pertaining to each system's ability to integrate information from arbitrary new data sources, however, both systems generally required new sources to either already conform to pre-specified ontologies, or have the user specify such a mapping manually.

@@

\section{Pre-studies: Identifying Needs and Challenges}

@@

In summary, while data records ranged in complexity, no source subsumed the rest; all contained unique properties other sources did not have.  Moreover, the most common types of heterogeneity exhibited were terminological and value-related, which occurred vastly more than structural or modeling issues.
